Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Updated abstract

%%
To understand how data resolution impacts inference on mixed fisheries
interactions, we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on population targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\ 
%%
Fifty years of sub-daily fishing was simulated and used to draw inference on
the underlying community structures. We compared inferences based on:
commercial catch, a simulated fixed-site sampling survey design and the true
underlying community. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.
\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. We conclude from our example framework
application that commercial data, while containing bias, provide a useful tool
for managing catches in mixed fisheries if applied at the correct
spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE
SENTENCES ON KEY TAKE-HOME RESULTS]\\
%%
\end{abstract}

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions.
As fishers do not have full control over what species they select in `mixed
fisheries' this can result in catch of low quota or protected species. If
fishers discard over-quota catch of a species for which they have no quota, it
limits our ability to control fishing mortality \citep{Alverson1994,
	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
biological and economic sustainability \citep{Ulrich2011a, Batsleer2015}.\\

>>>>

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on population targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true underlying populations. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.
\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\

We conclude from our example framework application that commercial data, while
containing bias, provide a useful tool for managing catches in mixed fisheries
if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

@@

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions.
As fishers do not have full control over what species they select when fishing
in `mixed fisheries' it can result in catch of low quota or protected species.
If over-quota catch of a species for which they have no quota is discarded
without being accounted for it limits our ability to control fishing mortality
\citep{Alverson1994, Crowder1998, Rijnsdorp2007} and the ability to manage
fisheries for the biological and economic sustainability \citep{Ulrich2011a,
	Batsleer2015}.\\
